---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
devtools::load_all(".")
```

scCNVis is an R package for exploring single-cell copy number data. All plotting
functions take as input an `scCNVisObject`. Example data has been provided
to show how this is done, as described below. The primary method for creating
a `scCNVisObject` requires you to manually specify multiple inputs, but helper 
functions exist to directly import output formats from some popular CNV calling tools
(see bottom of this page for details).

##Default method

For the default method, you first need an input matrix containing the copy number
values. Here, we use the provided example data, which is adapted from the example
data provided by the infercnv package.

```{r setup}
library(scCNVis)

#Example matrix
#Rows = cells, Columns = Genomc regions, Values = Copy number values (or a similar metric)
#Row names and column names are optional, because the cell names and column
#info will be provided separately

#In this example, the provided matrix uses genes as column names. The column
#names can be anything that you want, as long as they correspond to regions in
#the genome described by the GenomicRanges object provided (below)
matrix <- example.matrix
print(dim(matrix))
print(matrix[1:5,1:5])
```

Second, is the example cell names:
```{r}

cells <- example.cells
#The number of cell names should be the same as the number of rows as the input
#matrix, and should be in the same order as those rows
print(length(cells))
print(cells[1:5])
```

Third, is a `GenomicRanges::GRanges` object. It should have the same length
as the number of columns in the input matrix, where each entry describes
a genomic bin. Bins are expected to be region-sorted and non-overlapping.
```{r}
granges <- example.granges
print(granges)
```

Finally, is the input meta data. This is a data.frame where each row
corresponds to a cell. At a minimum, this should have a `Sample` column
describing what sample the cell came from, but can include an arbitrary amount of
other data as well. In this example, our meta data also includes subclone identifiers
generated by infercnv. Row names should be the provided cell names and correspond
to the provided cell matrix. The matrix and meta data are expected to be in the same
order.

```{r}
meta <- example.meta
print(head(meta))
```

These inputs can be used to create a `scCNVis` object:

```{r}
obj <- scCNVis::createPlotObject(input.matrix = matrix,
                                 cell.names = cells,
                                 granges = granges,
                                 meta = meta)

```

##Importing from infercnv

If CNV calls were generated using infercnv, it is possible to generate a `scCNVisObject`
directly from the resulting `run.final.infercnv.obj`. An example of such an object
has been included with scCNVis. It can be used to create a `scCNVisObject` as follows:

```{r}
#grab the provided example object
infercnv.obj <- example.infercnv.obj
obj <- scCNVis::createPlotObjectFromInfercnv(infercnv.obj = infercnv.obj,
                                             sample.name = "Example.Sample")
```

See the additional documentation articles about making frequency plots, heatmaps
and line plots for examples of how to use the `scCNVis` object.