---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
devtools::load_all(".")
```

scCNVis is an R package for exploring single-cell copy number data. All plotting
functions take as input an `scCNVis` object. Example data has been provided
to show how this is done, as described below:

First, is the example input matrix containing the copy number values:

```{r setup}
library(scCNVis)

#Example matrix
#Rows = cells, Columns = Genomc regions, Values = Copy number values (or a similar metric)
#Row names and column names are optional, because the cell names and column
#info will be provided separately
matrix <- example.matrix
print(dim(matrix))
print(matrix[1:5,1:5])
```

Second, is the example cell names:
```{r}

cells <- example.cells
#The number of cell names should be the same as the number of rows as the input
#matrix, and should be in the same order as those rows
print(length(cells))
print(cells[1:5])
```

Third, is a `GenomicRanges::GRanges` object. It should have the same length
as the number of columns in the input matrix, where each entry describes
a genomic bin. Bins are expected to be region-sorted and non-overlapping.
```{r}
granges <- example.granges
print(granges)
```

Finally, is the input meta data. This is a data.frame where each row
corresponds to a cell. At a minimum, this should have a `Sample` column
describing what sample the cell came from, but can include an arbitrary amount of
other data as well. Row names should be the provided cell names.

```{r}
meta <- example.meta
print(dim(meta))
print(head(meta))
```

These inputs can be used to create a `scCNVis` object.

```{r}
obj <- scCNVis::createPlotObject(input.matrix = matrix,
                                 cell.names = cells,
                                 granges = granges,
                                 meta = meta)

```

See the additional documentation articles about making frequency plots, heatmaps and line plots for examples of how to use the `scCNVis` object.
show how to use this object to generate plots.